The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-11 paper.tex
More clean-up in Sections 5 and 6.

The degree of control over single photons has also improved. Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, new ways to engineer entangled quantum states and implement quantum operations have been discovered. These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time. We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings.

@@

%With the advent of faster optical components, and single-photon 
%detectors, it has become feasible to perform any single qubit 
%operation, and a post-selected CPHASE gate on time-bin qubits 
%\cite{bib:Humphreys2013}. These gates form an universal set for 
%quantum computing. At the same time, an ultrafast measurement 
%technique for recovering time-bin qubits was also demonstrated 
%\cite{bib:Donohue2013}.

%In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin 
%qubits have a polarization register which is used to toggle between 
%the mode in which qubits are stored and transmitted, {\it i.e.} the 
%`register' mode, and the mode in which qubits are manipulated, {\it 
%i.e.} the `processing' mode using a polarization rotation. Other 
%operations needed are a displacement operation, that moves a time-
%bin qubit in the processing polarization in time relative to other 
%qubits, a partial polarization rotation between the register and 
%processing polarizations to couple them, and a photon number 
%measurement in a bin. The polarization rotation and polarization 
%coupling operations were implemented using a fast integrated 
%optical switch based on polarization-sensitive cross-phase 
%modulation with a switching time of less than 10ps. The 
%displacement was implemented using a calcite crystal of a size that 
%is of a path-length difference equal to an integer multiple of the 
%time-bin separation. Using these operations and post-selection 
%using a single-photon detectors, the authors were able to perform a 
%heralded CPHASE gate \cite{bib:KLM01}.

@@

Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}. Such states are produced by a standard laser source, thus reducing experimental resources. The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port. The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them. The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively. The output intensity at the $j$th port is then
\begin{align}
I_k=I(r_{1k}^2+r_{jk}^2+2 r_{1k}r_{kj}\cos(\phi+\theta_{jk})) \ ,
\end{align}
where $\theta_{jk}=0$ for $k=1$. By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$. An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$. In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.

@@

An EPR pair, or Bell pair, is one of the four states,
\begin{align}
\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \\
\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
\end{align}
which are all maximally entangled and locally equivalent to one another. These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}. In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.} successfully prepared only under certain measurement outcomes of auxiliary modes. Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}. They are often used as a building block for preparing other multipartite entangled states.

@@

These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with CPHASE operation applied between edges, as shown in Fig.~\ref{fig:cluster}. For this reason, such states are also referred to as graph states. The CPHASE operations generate entanglement between the qubits, and because they commute, are independent of ordering. Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC). Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}. Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\columnwidth]{cluster_state}
\caption{The representation of cluster states as a graph. Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}	
\end{figure}

Unfortunately, implementing CPHASE gates using linear optics is complicated and highly non-deterministic. A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis. These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process. These operations are shown in Fig.~\ref{fig:fusion}. Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing CPHASE gates. Furthermore, unlike CPHASE gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing CPHASE gate implementations, a major experimental simplification.

Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing CPHASE gates.

@@

The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters. This corresponds to a direct implementation of the Reck \emph{et al.} decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.

@@

Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them. In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains, shown in Fig.~\ref{fig:FL_arch}.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.5\columnwidth]{full_architecture}
\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$. The pulse-train then enters a dual-loop configuration. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes). The architecture is controlled via three dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train. The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}	
\end{figure}

@@

The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary. It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described earlier.

@@

The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward. To address this, it was shown in \cite{Rohde} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.

@@

Broadly speaking, there are two main classes of photodetectors: non-photon-number-resolving (also referred to as bucket, or on/off) detectors, and photon-number-resolving (PNR) detectors. As the names suggest, non-PNR detectors only detect the presence or absence of photons in an incident beam, while PNR detectors are able to measure its number of photons. The outcomes of a PNR detector are described by the measurement projectors,
\begin{align}
\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,\nonumber \\	
\end{align}
while those of the non-photon-number-resolving detectors are given by
\begin{align}
\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on}\ .
\end{align}

The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number. In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic. However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer. Other common problems that plague these detectors are dark counts which add spurious counts from the background, and dead-time which causes the detector to lose counts during a period when it is inactive immediately after the detection of photons.

\subsubsection{Non-photon-number-resolving detectors}
The first type of non-PNR detectors are photomultiplier tubes (PMTs). A PMT comprises of a vacuum tube with a photocathode for light absorption. The photoelectric effect then releases electrons in the photocathode, and this current is multiplied by a cascade of secondary electron emissions from a series of electrodes. This amplified signal can be picked up to indicate the presence of photons.

@@

\subsection{Linear optics quantum computation (LOQC)}
With the advancement in single-photon state preparation, detectors and quantum interferometers, quantum computation using linear optics has become feasible. 
For universal quantum computation using linear optics and single photon inputs, nonlinear couplings between the different optical modes are needed. Photons, being bosons, do not interact with one another like the way fermions do. Hence, some careful engineering has to be done in order to achieve this nonlinear coupling between modes. Some of the methods used to introduce this nonlinearity include measurements and feedforwarding \cite{bib:KLM01}, and  photon-atom interactions \cite{bib:Brod16}. These nonlinearities have been used to construct entangling gates required for (approximate) universality in quantum computation using the circuit model. They have also been used to construct entangled graph states, like the cluster states covered in Section \ref{section:cluster}, that are used in MBQC. Comprehensive reviews have been written previously to cover this topic \cite{bib:Kok05,bib:JW12}, hence we will skip some basic information to focus on recent advances. There are multiple challenges to implementing a scalable, fully-optical quantum computer, and progress has been focused on overcoming these challenges. In this section, we will discuss a few of these challenges, and the advances that have been made to overcome them.

\subsubsection{Challenges and Progress in LOQC}
To date, the quantum computation still requires the use of non-deterministic operations, each of which succeeds with less than unity probability and has to be run many times before a single try succeeds. Moreover extra qubits are needed for error correction. These requirements put an overhead on the computational cost, in particular at the single photon production stage where a high rate of production of multiple photons is desired for this purpose. Second, feed-forwarding requires detectors with very fast response time. In feedforward control, one mode is measured and then some operation that depend on the measurement outcome are effected on other modes. The readout from the measurement has to happen before the light beam in the target modes passes. The last challenge is that of loss. Loss can happen anywhere in the linear optical network, but is especially problematic in coupling between different mediums, and upon absorption of a photon in a detector. Loss causes computations to fail. In the case that this error is detectable, the computation would have to be repeated. If not, the computation returns a wrong result.

@@

 Such Kerr nonlinearities are usually implemented on states of light via atom-photon interactions. Whether such cross-Kerr nonlinearities on single photon will help LOQC is a subject of debate. On one side, the arguments in the negative come down to fundamental noise limits in atom-photon interactions using phenomenological model of a cross-Kerr medium \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}. On the other hand, an example of a CPHASE gate using photons that counterpropagate through multiple atom-mediated cross-Kerr interaction sites has been constructed, and theoretically shown to work via a first principle treatment of the multimode light field and atomic medium \cite{bib:Brod16}. Regardless of who is right in this debate, increments in the strength of Kerr nonlinearities have been achieved in the last five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, and this avenue remains a tantalizing possibility for deterministic quantum gates.

>>>>

The degree of control over single photons has also improved. Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, new ways to engineer entangled quantum states and implement quantum operations have been discovered. These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time.

We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings. Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters. We discuss this, and an analogous decomposition for single photons with additional internal states, in Section \ref{sec:decomp}.

@@

%With the advent of faster optical components, and single-photon 
%detectors, it has become feasible to perform any single qubit 
%operation, and a post-selected {\sc cphase} gate on time-bin qubits 
%\cite{bib:Humphreys2013}. These gates form an universal set for 
%quantum computing. At the same time, an ultrafast measurement 
%technique for recovering time-bin qubits was also demonstrated 
%\cite{bib:Donohue2013}.

%In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin 
%qubits have a polarization register which is used to toggle between 
%the mode in which qubits are stored and transmitted, {\it i.e.} the 
%`register' mode, and the mode in which qubits are manipulated, {\it 
%i.e.} the `processing' mode using a polarization rotation. Other 
%operations needed are a displacement operation, that moves a time-
%bin qubit in the processing polarization in time relative to other 
%qubits, a partial polarization rotation between the register and 
%processing polarizations to couple them, and a photon number 
%measurement in a bin. The polarization rotation and polarization 
%coupling operations were implemented using a fast integrated 
%optical switch based on polarization-sensitive cross-phase 
%modulation with a switching time of less than 10ps. The 
%displacement was implemented using a calcite crystal of a size that 
%is of a path-length difference equal to an integer multiple of the 
%time-bin separation. Using these operations and post-selection 
%using a single-photon detectors, the authors were able to perform a 
%heralded {\sc cphase} gate \cite{bib:KLM01}.

@@

Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}. Such states are produced by a standard laser source, thus reducing experimental resources. The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port. The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them. The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively. The output intensity at the $k$th port is then
\begin{align}
I_k=I(r_{1k}^2+r_{jk}^2+2 r_{1k}r_{kj}\cos(\phi+\theta_{jk})) \ ,
\end{align}
where $\theta_{jk}=0$ for $k=1$, and $I$ is the intensity of the input coherent states. By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$. An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$. In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.

@@

An EPR pair, or Bell pair, is one of the four states,
\begin{align}
\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \ {\rm and} \\
\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
\end{align}
which are all maximally entangled and locally equivalent to one another. These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing.
%\cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.~}successfully prepared only under certain measurement outcomes of auxiliary modes. Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.

@@

These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with {\sc cphase} operation applied between edges, as shown in Fig.~\ref{fig:cluster}. For this reason, such states are also referred to as graph states. The {\sc cphase} operations generate entanglement between the qubits, and because they commute, are independent of ordering. Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC). Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}. Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.3\columnwidth]{cluster_state}
\caption{The representation of cluster states as a graph. Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on {\sc cphase} gates, the ordering of which is irrelevant.} \label{fig:cluster}	
\end{figure}

Unfortunately, implementing {\sc cphase} gates using linear optics is complicated and highly non-deterministic. A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis. These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process. These operations are shown in Fig.~\ref{fig:fusion}. Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing {\sc cphase} gates. Furthermore, unlike {\sc cphase} gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing {\sc cphase} gate implementations, a major experimental simplification.

Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing {\sc cphase} gates.

@@

The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters. This corresponds to a direct implementation of the Reck \emph{et al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.

@@

Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them. In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the 
number of optical modes). The architecture is controlled via three 
dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, 
keep it within the outer loop for the required duration, and then couple 
out of the outer loop, yielding the transformed pulse-train. The central 
beamsplitter must be able to implement arbitrary classically-controlled 
beamsplitter operations.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.4\columnwidth]{full_architecture}
\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
%The source prepares the temporally encoded pulse-train, with time-bin 
%separation $\tau$.
%The pulse-train then enters a dual-loop configuration. The inner loop has 
%%length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is 
%the number of optical modes). The architecture is controlled via three 
%dynamically controlled beamsplitters. The first and last need only be on/
%off switches, whose sole purpose is to couple in the prepared pulse-
%train, keep it within the outer loop for the required duration, and then 
%couple out of the outer loop, yielding the transformed pulse-train. The 
%central beamsplitter must be able to implement arbitrary classically-
%controlled beamsplitter operations.
} \label{fig:FL_arch}	
\end{figure}

@@

The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary. It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described in Section \ref{sec:decomp}.

@@

The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward. To address this, it was shown in \cite{Rohde15} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.

@@

Broadly speaking, there are two main classes of photodetectors: non-photon-number-resolving (also referred to as bucket, or on/off) detectors, and photon-number-resolving (PNR) detectors. As the names suggest, non-PNR detectors only detect the presence or absence of photons in an incident beam, while PNR detectors are able to measure its number of photons. The outcomes of a PNR detector are described by the measurement projectors,
\begin{align}
\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,
\end{align}
while those of the non-photon-number-resolving detectors are given by
\begin{align}
\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on}\ .
\end{align}
The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number. In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic. However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer. Other common problems that plague these detectors are dark counts which add spurious counts from the background, and dead-time which causes the detector to lose counts during a period when it is inactive immediately after the detection of photons.

\subsubsection{Non-photon-number-resolving (non-PNR) detectors}
The first type of non-PNR detectors are photomultiplier tubes (PMTs). A PMT comprises of a vacuum tube with a photocathode for light absorption. The photoelectric effect then releases electrons in the photocathode, and this current is multiplied by a cascade of secondary electron emissions from a series of electrodes. This amplified signal can be picked up to indicate the presence of photons.

@@

\subsection{Linear optics quantum computation (LOQC)}
With the advancement in single-photon state preparation, detectors and quantum interferometers, quantum computation using linear optics has become feasible. 
For universal quantum computation using linear optics and single photon inputs, nonlinear couplings between the different optical modes are needed. Photons, being bosons, do not interact with one another like the way fermions do. Hence, some careful engineering has to be done in order to achieve this nonlinear coupling between modes. Some of the methods used to introduce this nonlinearity include measurements and feedforwarding \cite{bib:KLM01}, and  photon-atom interactions \cite{bib:Brod16}. These nonlinearities have been used to construct entangling gates required for (approximate) universality in quantum computation using the circuit model. They have also been used to construct entangled graph states, like the cluster states covered in Section \ref{section:cluster}, that are used in MBQC. Comprehensive reviews have been written previously to cover this topic \cite{bib:Kok05,bib:JW12}, hence we will skip some basic information to focus on recent advances. There are multiple challenges to implementing a scalable, fully-optical quantum computer, and progress has been focused on overcoming these challenges. We will discuss a few of these challenges, and the advances that have been made to overcome them.

To date, the quantum computation still requires the use of non-deterministic operations, each of which succeeds with less than unity probability and has to be run many times before a single try succeeds. Moreover extra qubits are needed for error correction. These requirements put an overhead on the computational cost, in particular at the single photon production stage where a high rate of production of multiple photons is desired for this purpose. Second, feed-forwarding requires detectors with very fast response time. In feedforward control, one mode is measured and then some operation that depend on the measurement outcome are effected on other modes. The readout from the measurement has to happen before the light beam in the target modes passes. The last challenge is that of loss. Loss can happen anywhere in the linear optical network, but is especially problematic in coupling between different mediums, and upon absorption of a photon in a detector. Loss causes computations to fail. In the case that this error is detectable, the computation would have to be repeated. If not, the computation returns a wrong result.

@@

 Such Kerr nonlinearities are usually implemented on states of light via 
 atom-photon interactions. Whether such cross-Kerr nonlinearities on 
 single photon will help LOQC is a subject of debate. On one side, the 
 arguments in the negative come down to fundamental noise limits in atom-
 photon interactions using phenomenological model of a cross-Kerr medium 
 \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}. On the other 
 hand, an example of a {\sc {\sc cphase}} gate using photons that 
 counterpropagate through multiple atom-mediated cross-Kerr interaction 
 sites has been constructed, and theoretically shown to work via a first 
 principle treatment of the multimode light field and atomic medium 
 \cite{bib:Brod16}. Regardless of who is right in this debate, increments 
 in the strength of Kerr nonlinearities have been achieved in the last 
 five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, 
 and this avenue remains a tantalizing possibility for deterministic 
 quantum gates.
